%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Xuan Cuong Ho} & Email : \href{mailto:cuong1181998@gmail.com}{cuong1181998@gmail.com}\\
  Blockchain Engineer & Mobile : \href{tel:+84357735333}{+84-35-773-5333} \\
  & Github : \href{https://github.com/cuong1181998}{github/cuong1181998} \\
  & Linked In : \href{https://www.linkedin.com/in/cuonghx110898}{linkedin/cuonghx110898} \\
  & Blog : \href{https://0xcuonghx.netlify.app/}{https://0xcuonghx.netlify.app/} \\
\end{tabular*}

%-----------ABOUT-----------------
\section{About}
  {I'm a full-stack developer with many years of experience in Web Development since 2018, mostly using Javascript.} \\ \smallskip
  {Now I develop and researching the EVM-compatible ecosystem.} \\ \smallskip
  {I have good understanding at fundamental of computer science Data structure and Algorithms, Programming Paradigm, Cryptography, Database Design, etc} \\ \smallskip
  {I have problem-solving skills and can work independently or in teamwork.} \\ \smallskip
  {I'm looking for challenging jobs, learning new technology to solve problems.} \\
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hanoi University of Science and Technology}{Hanoi, Vietnam}
      {Engineer of Information Technology;  GPA: 3.03}{Sep. 2016 -- May. 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {G.U Technologies}{Remote, Japan}
      {Blockchain Engineer}{Mar 2022 - Present}
      \resumeItemListStart
        \resumeItem{Smart contract developer}
          {ERC20, ERC721, etc}
        \resumeItem{Building dapps based on EVM-compatible chain }
          {NFT marketplace, NFT bridge, etc}
        \resumeItem{Building related tools, SDK}
          {Wallet Connector, etc}
        \resumeItem{Skills}
        {Solidity, React, Next.js, The Graph, NestJS}
      \resumeItemListEnd

    \resumeSubheading
      {FPT Telecom International}{Hanoi, Vietnam}
      {Software Engineer}{Apr 2021 - Feb 2022}
      \resumeItemListStart
        \resumeItem{Web developer}
          {Building a live-stream platform combined with a sale management system}
        \resumeItem{Skills}
        {Nodejs, Apache Kafka, NestJS, React.js, MongoDB, Microservices}
      \resumeItemListEnd

    \resumeSubheading
      {ICTS custom software}{Hanoi, Vietnam}
      {Software Engineer}{Aug 2020 - Apr 2021}
      \resumeItemListStart
        \resumeItem{Web developer}
          {Outsourcing base on requirements}
        \resumeItem{Skills}
        {NestJS, React.js }
      \resumeItemListEnd

    \resumeSubheading
      {FPT Telecom International}{Hanoi, Vietnam}
      {Intern}{Apr 2019 - Aug 2020}
      \resumeItemListStart
        \resumeItem{Web developer}
          {Building enterprise management system on web service}
        \resumeItem{Skills}
        {React.js, Node.js, MongoDB, Microservices}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{NFT marketplace}
      {Market platform buy and sell NFT on EVM-compatible chain.}
    \resumeSubItem{NFT marketplace}
      {Platform bridging NFT on between two EVM-compatible chains.}
    \resumeSubItem{Livestream e-commerce}
      {Platform live stream and sell products combine with sale management, shipping.}
    \resumeSubItem{Enterprise management system}
      {Microservice support enterprise management system such as IAM, CRM, Booking, etc}
    \resumeSubItem{Receipt management base on ORC}
      {Platform allow user capture receipt and manage monthly budget}
    \resumeSubItem{Information Retrieval}
      {Build crawler and search engine base on Solr}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
  \resumeSubItem{Programing Languages}
  {Javascript, Solidity}
  \resumeSubItem{Database}
  {MongoDB, MySQL, Postgresql}
  \resumeSubItem{Protocol}
  {RestFul, GraphQl, Socket, MessageQueue}
  \resumeSubItem{Software Architecture}
  {Microservice, MVC}
  \resumeSubItem{Framework}
  {ReactJS, NextJS, NestJS, SocketIO, Apache Kafka, RabbitMQ}
  \resumeSubItem{Services}
  {The Graph}
 \resumeSubHeadingListEnd

%--------LANGUAGE SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
  \resumeSubItem{English}
  {Professional working proficiency}
  \resumeSubItem{Vietnamese}
  {Native or bilingual proficiency}
 \resumeSubHeadingListEnd

%--------AWARDS------------
\section{Awards}
  \begin{itemize}[leftmargin=*]
    \item Mathematics competition in Vinh City in 2013
  \end{itemize}
%-------------------------------------------
\end{document}
